\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{SE 3XA3: SRS\\ohm Resistor Scanner}

\author{Team \# 4, ohm
		\\ Ryan Marks (marksr2)
		\\ Graeme Crawley (crawleg)
		\\ Jonathan Brown (brownjs2)
}


\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2016-09-26 & Ryan & Created template with section headings\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle



\section{Project Drivers}

\subsection{The Purpose of the Project }
\subsection{The Stakeholders}


\section{Project Constraints}

\subsection{Mandated Constraints}
\subsection{Naming Conventions and Terminology }
\subsection{Relevant Facts and Assumptions}


\section{Functional Requirements}

\subsection{The Scope of the Work}

\subsubsection{The Current Situation}

Electronics hobbyists will use resistors in almost any project they encounter.
Currently there are a few ways they can identify the resistance of the resistors, these methods are as follows:
\begin{itemize}

\item Manual Method
\subitem The resistor colour code was developed to allow the ease of reading for people. 
With practise, people can quickly identify resistors by the colour bands, however this is less helpful when searching  for a specific resistor.
Additionally building proficiency takes time and can be a frustrating slowdown for a beginner, especially if they misidentify components during assembly.

\item Organizational Method
\subitem By storing resistors according to their resistances it becomes a trivial exercise to find a resistor of a given resistance.
This method is clearly superior in professional environments where very large numbers of resistors are on hand.

\item Meter Method
\subitem The current technique of choice for individuals who cannot discern colour codes is to measure a given resistor with a resistance meter.
This technique is immediately faster than reading colour bands, however it is somewhat laborious to have to pick up and test individual components.

\end{itemize}

\subsubsection{The Context of The Work}

This work has a very limited context, it serves as a tool to any person using colour band resistors who feels it useful.
There are not other subject matter domains that need to be understood or integrated with, beyond the resistor colour codes.

\subsubsection{Work Partitioning}

This work does not need to respond to any external business events, this section is not relevant

\subsection{Business Data Model \& Data Dictionary}
\subsection{The Scope of the Product}

\subsubsection{Product Boundary}


\subsection{Functional Requirements}


\section{Non-functional Requirements}

\subsection{Look and Feel Requirements }
\begin{enumerate}
\item The application shall have a very minimal user interface focussed primarily around the view of the camera.
\end{enumerate}
\subsection{Usability and Humanity Requirements}
\begin{enumerate}
\item The application shall be easily usable by people aged 8 to 70.
\item The application shall be suitable for a user with a minimal understanding of resistor colour codes and very little training.
\item The application shall not require the understanding of any particular language as all options symbolically.
\item The application shall be usable by those with colour blindness.
\end{enumerate}
\subsection{Performance Requirements}
\subsubsection{Speed and Latency Requirements}
\begin{enumerate}
\item The application should launch in no more than 5 seconds.
\item The algorithm used to process the income stream of images should be able to process between 15 and 30 images per second on a standard mobile phone.
\end{enumerate}
\subsubsection{Precision or Accuracy Requirements}
\begin{enumerate}
\item The application should identify an input as the correct class of resistor 95\% of the time.
\end{enumerate}
\subsubsection{Reliability and Availability Requirements}
\begin{enumerate}
\item The application will not require internet access.
\end{enumerate}
\subsection{Operational and Environmental Requirements}
\begin{enumerate}
\item
\end{enumerate}
\subsection{Maintainability and Support Requirements}
\begin{enumerate}
\item
\end{enumerate}
\subsection{Security Requirements}
\begin{enumerate}
\item
\end{enumerate}
\subsection{Cultural Requirements}
\begin{enumerate}
\item
\end{enumerate}
\subsection{Legal Requirements}
\begin{enumerate}
\item
\end{enumerate}

\section{Project Issues}

\subsection{Open Issues }
\subsection{Off-the-Shelf Solutions}
\subsection{New Problems}
\subsection{Tasks}
\subsection{Migration to the New Product}
\subsection{Risks}
\subsection{Costs}
\subsection{User Documentation and Training}
\subsection{Waiting Room}
\subsection{Ideas for Solutions}


\end{document}